%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper]{twentysecondcv} % a4paper for A4

\usepackage{natbib}
%\usepackage[natbibapa]{apacite}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\profilepic{./images/bernd} % Profile picture

\cvname{Bernd Malle} % Your name
\cvjobtitle{SW Developer} % Job title/career

\cvdate{8 October 1979} % Date of birth
\cvaddress{Graz, Austria} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{+43 6781275414} % Phone number
\cvsite{http://berndmalle.com} % Personal website
\cvmail{bernd.malle@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 ABOUT ME
%----------------------------------------------------------------------------------------

\aboutme{
	Bernd is an enthusiastic Software guy interested in combining client-side (Web) development with algorithmic problem solving. He is currently applying his skills to creating Lemontiger, a next-generation team collaboration tool fueled by a graph-based resource recommender. 
	Although Bernd left his academic work for entrepreneurial challenges, he retained a scientific mind-set and sound, experimental approach.
} % To have no About Me section, just remove all the text and leave \aboutme{}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{
	{Think of more/2.0},
	{Python/3.5},
	{Graph Theory/4.0},
	{Lean thinking/4.4},
	{SW Architecture/4.8},
	{Java- \& Typescript/5.2},
	{client-side development/5.7}}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6
% \skillstext{{lovely/4},{narcissistic/3}}

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 INTERESTS
%----------------------------------------------------------------------------------------

\section{Interests}



%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2016-2018}{Ph.D. {\normalfont candidate in Computer Science}}{TU Graz}{\emph{Research in privacy-aware Machine Learning}, ongoing}
	\twentyitem{2014-2016}{M.Sc. software engineering }{TU Graz}{Thesis in \emph{Graphinius - an online graph exploration platform}}
	\twentyitem{2005-2014}{B.Sc. software engineering \& business administration}{TU Graz}{Thesis in \emph{graph extraction from image data}}
	\twentyitem{2002-2005}{Studies of Economics}{KF University, Graz}{Special interest in political economics; not graduated}
	\twentyitem{1999-2002}{Abendmatura @ College of further education}{Graz, Austria}{Specializing in mathematics and physics.}
	\twentyitem{1997-1998}{ITCP Information Technology Certified Professional}{Wifi Graz}{}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{2018}{\citeyearpar{Need4Speed} The Need for Speed. Comparison of JS vs. C++ - generated ASM.js / WASM}
	\twentyitemshort{2017}{\citeyearpar{InteractiveAnonymization} Interactive Anonymization for Privacy aware Machine Learning}
	\twentyitemshort{2017}{\citeyearpar{FedPaper} The more the merrier - federated learning from local sphere recommendations}
	\twentyitemshort{2017}{\citeyearpar{PAML2} Do not disturb? - classifier behavior on perturbed datasets}
	\twentyitemshort{2016}{\citeyearpar{PAML1} The Right to be forgotten. Towards Machine Learning on perturbed knowledge bases}
	
%	\cite{PAML1}
%	\cite{Need4Speed}
	
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}

%----------------------------------------------------------------------------------------
%	 CONFERENCES
%----------------------------------------------------------------------------------------

\section{Conference talks}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitemshort{2017}{ECML - European Conference on Machine Learning, Skopje, Macedonia}
	\twentyitemshort{2017}{CD-MAKE - Cross disciplinary ML and Knowledge Extraction, Reggio Calabria, Italy}
	\twentyitemshort{2017}{ARES - Conference on Availability, Reliability and Security, Reggio Calabria, Italy}
	\twentyitemshort{2017}{Security Forum Hagenberg, Linz, Austria}	
	\twentyitemshort{2016}{ÖGAI (Austrian society for AI) Meeting , Klagenfurt, Austria}
	\twentyitemshort{2016}{ARES - Conference on Availability, Reliability and Security, Salzburg, Austria}
	%\twentyitemshort{<dates>}{<title/description>}
\end{twentyshort}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2016-2018}{ Member of the Austrian KIRAS funded project Darknet.
	}{Project}{}
	\twentyitem{2015-2018}{ Employee at Secure Business Austria (SBA) Research GmbH, Vienna, Austria.
	}{Project}{}
	\twentyitem{2014-2018}{ Member of the HCI-KDD research group at Medical University Graz, Austria.
	}{Research}{}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Other information}

\subsection{Review}

Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

%----------------------------------------------------------------------------------------
%	 SECOND PAGE EXAMPLE
%----------------------------------------------------------------------------------------

\newpage % Start a new page

\makeprofile % Print the sidebar

\section{Other information}

\subsection{Review}

Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

\section{Other information}

\subsection{Review}

Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

%----------------------------------------------------------------------------------------

%\bibliographystyle{apacite}
\bibliography{references}

\end{document} 
